MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
...

>>>>

```{r}
# Find shooting percentage of each match

# Trying to reshape...

library(reshape)
game <- cast(data = df, GAME_ID1 ~ SHOT_RESULT)
View(game)

#

Team <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
FG_Percentage <- rep(NA, (lastGamesID - firstGamesID + 1) * 2)
for(i in 21400001:21400908){
  j = i - 21400001 +1 # 
  game <- df[, df[, "GAME_ID1"] == i]
  home <- game[, game["LOCATION"] == "H"]
  home.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / nrow(home)
  away <- game[, game["LOCATION"] == "A"]
  away.p <- count(home[, home[, "SHOT_RESULT"] == 1]) / away(home)
  FG_Percentage[j] <- home.p
  FG_Percentage[j + 1] = away.p
  Team[j] = "H"
  Team[j + 1] = "A"
}
